---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fevdid

<!-- badges: start -->
[![R-CMD-check](https://github.com/vfci/fevdid/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/vfci/fevdid/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

R package to identify structural VAR shocks using maximization of explained forecast error variances. Implemented to target either the time domain or frequency domain.

## Installation

You can install the development version of fevdid from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("VFCI/fevdid")
```

## Usage

This is a basic example which shows you how to solve a common problem:

```{r example}
library(fevdid)
## basic example code
```

## References

[Chapter 6: "Forecast error variance maximization"](https://jrenne.github.io/IdentifStructShocks/forecast-error-variance-maximization.html) of the book *The Identification of Dynamic Stuctural Shocks*, by Jean-Paul Renne and Kenza Benhima.

- [jrenne Github](https://github.com/jrenne)

Explains and codes up an example of identifying a shock that maximizes forecast error variance contribution.